Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-23 CONCUR2018/paper.tex
nudge

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  However, in
order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and
$\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
certain properties of the plant hold at any given point in time.  In order
to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model_semantics} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
$t=T$. \textcolor{red}{[ADD REFERENCE TO PUBLISHED WORK ON ABSTRACT ACCELERATION.]}

@@

In the second stage, we take the complex eigenvalue with the largest angle, 
which is characterised by $\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)|, \lambda
\in \Lambda\}$, and reduce its imaginary component only ($re(\lambda) + f\,
im(\lambda)$ such that the new controller satisfies $\phi_\mathit{init}^K$). 
The process ends when no imaginary part can be further reduced.  The
resulting closed loop form converges faster than the original and has a
smaller rotation, which facilitates meeting the safety specification
$\phi_\mathit{safety}$.

@@

With respect to the additional complexity introduced by the synthesis
of observer-based controllers compared to fully observed systems, we
found that on average, observer synthesis is over an order of
magnitude slower than full state controller synthesis for the given
benchmarks. This is due to the fact that the introduction of the
observer doubles the order of the model.

>>>>

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  However, in
order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and
$\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
certain properties of the plant hold at any given point in time.  In order
to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model_semantics} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
$t=T$, and then use abstraction~\cite{JSS14,cattaruzza2015unbounded} to overapproximate $\hat{X}_n$.

@@

In the second stage, we take the complex eigenvalue with the largest angle, 
which is characterised by $\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)|, \lambda
\in \Lambda\}$, and reduce its imaginary component only ($re(\lambda) + f\,
im(\lambda)$ such that the new controller satisfies $\phi_\mathit{init}^K$). 
The process ends when no imaginary part can be further reduced.  The
resulting closed loop form converges faster than the original and has a
smaller rotation, which facilitates meeting the specification
$\phi_\mathit{safety}$.

@@

Given the nature of the specifications, observer synthesis cannot be directly compared to full state controller synthesis. 
On average, we found the former to be over an order of magnitude slower for the given benchmarks, largely due to the fact that the introduction of the
observer doubles the order of the model.
